Efficient Selection of Time Series Shapelets

### 2024-04-17 Docs/paper/main.tex
Add clustering example

@@

Notice that our definition of the silhouette, the term $b$ considers all
subsequences from other classes instead of only considering only the class that
is closest to the subsequence $S_i$.

\section{Approach}
The bottleneck of the computation is in the evaluation part, where, in order to
compute the Silhouette score (also for the F-statistic and all other measures),
all pairs of distances have to be computed. To avoid that, we will use the fact
that shapelets that have a high silhouette score are of good quality for time
series classification. Since we know, in a clustering setup, silhouette is high
when he clusters are compact and far from each other, then the problem of
finding good quality shapelets reduces to finding clusters with high silhouette
scores.

We start by extracting the set of sliding windows $W$ from all the time series
$W = \bigcup_T W_T^l$, then we cluster all the windows in $W$.
For each cluster $C_i$, we assign a label $c$ using a majority vote, i.e., the
label of cluster $C_i$ is the label of the set with largest cardinal, consisting
of windows assigned to cluster $C_i$ that have the same class label.

>>>>

\newcommand{\mc}[1]{\textcolor{teal}{ --- MC: #1 --- }}
\newcommand{\ac}[1]{\textcolor{orange}{ --- AC: #1 --- }}
\newcommand{\jg}[1]{\textcolor{red}{ --- JG: #1 --- }}

@@

Notice that our definition of the silhouette, the term $b$ considers all
subsequences from other classes instead of only considering only the class that
is closest to the subsequence $S_i$. Next, a fixed number of subsequences from
each class are selected as shapelets, based on the highest score achieved.

\section{Approach}
The bottleneck of the computation is in the evaluation part, where, in order to
compute the Silhouette score (same for the F-statistic and the other measures),
all pairs of distances have to be computed. To avoid that, we will use the fact
that shapelets with a high silhouette score are of good quality for time
series classification. Since in a clustering setup, silhouette index of a 
cluster is high when the cluster is compact and far from other clusters, and 
the silhouette score of a cluster is simply the average of the silhouette 
scores of the subsequences in that cluster, then the subsequences with high 
silhouette are contained in the cluster.

\subsection{Clustering-based shapelets}
\begin{figure*}
  \includegraphics[width=\textwidth]{imgs/clustering.png}
  \caption{Sliding windows of length 40 from \emph{CBF} dataset, with centers
  (red dots) of 100 clusters using K-Means algorithm.\label{fig:clustering}}
\end{figure*}
We start by extracting the set of sliding windows $W$ from all the time series
$W = \bigcup_T W_T^l$, then we cluster all the windows in $W$.
For each cluster $C_i$, we assign a label $c$ using a majority vote, i.e., the
label of cluster $C_i$ is the label of the set with largest cardinal, consisting
of windows assigned to cluster $C_i$ that have the same class label.
Figure~\ref{fig:clustering} shows an example from the \emph{CBF} dataset plotted
on the plan by keeping only the first two PCA components. The gray dots in the
left sub-figure are the windows of length 40, and the red dots are the centers
of the clusters obtained y running K-Means algorithm with 100 clusters. The
right sub-figure shows the labels of the subsequences.
